---
title: "P8105_hw6"
author: "qz2492"
date: "2022-12-03"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(viridis)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 


## Problem 2

```{r}
homicide = read_csv('./data/homicide-data.csv') %>%
  janitor::clean_names()

```


#### Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. . For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

```{r}
prob2_df = 
  homicide %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    victim_age = as.numeric(victim_age),
    solved = as.numeric(disposition == "Closed by arrest")) %>% 
  filter(
    victim_race %in% c("White", "Black") &
    !(city_state %in% c("Dallas_TX", "Phoenix_AZ", " Kansas City_MO", "Tulsa_AL"))) %>% 
  select(city_state, solved, victim_age, victim_race, victim_sex)
```

#### For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
baltimore_df = prob2_df %>%
  filter(city_state == "Baltimore_MD")

baltimore_fit = glm(solved ~ victim_age + victim_sex + victim_race, family = binomial, data = baltimore_df) 
  
baltimore_fit %>%
  broom::tidy() %>%
  mutate(
    OR = exp(estimate),
    Conf_low = exp(estimate - 1.96 * std.error),
    Conf_high = exp(estimate + 1.96 * std.error)
  ) %>%
  filter(term == "victim_sexMale") %>%
  select(term, OR, Conf_low, Conf_high) %>%
  knitr::kable(digits = 4)

```

#### Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.
```{r}
all_fit = 
  prob2_df %>%
  nest(data = -city_state) %>%
  mutate(
    model = map(.x = data, ~glm(solved ~ victim_age + victim_sex + victim_race, family = binomial, data = .x)),
    result = map(model, broom::tidy)
  ) %>%
  unnest(result) %>%
  mutate(
    OR = exp(estimate),
    Conf_low = exp(estimate - 1.96 * std.error),
    Conf_high = exp(estimate + 1.96 * std.error)
  ) %>%
  filter(term == "victim_sexMale") %>%
  select(city_state, OR, Conf_low, Conf_high) 

all_fit %>%
  knitr::kable(digits = 4)
```

#### Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
all_fit %>%
  mutate(
    city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = OR, y = city_state)) +
  geom_point() +
  geom_errorbar(aes(xmin = Conf_low, xmax = Conf_high)) +
  labs(title = "The estimated ORs and CIs of solved cases for each city")
```

From the plot we can tell that not considering race and age, most cities in America have odds ratios lower than 1, which indicates male victims have lower odds than female victims to have their cases solved. Among those New York city has the smallest odds ratios, indicating male victims in NYC have the smallest chance to have their cases solved.

## Problem 3

#### Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).
```{r}
birthweight = read_csv('./data/birthweight.csv') %>%
  janitor::clean_names() %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) %>%
  select(-pnumsga, -pnumlbw) %>%
  drop_na() %>%
  relocate(bwt)
```

Except for `fincome`, all other variables are intuitive factors influencing a baby's birthweight owing to biological connections.

Let's take a look at the exploratory plots:
```{r}
numeric_variables = 
  birthweight %>%
  select(-babysex, -frace, -malform, -mrace)
GGally::ggpairs(numeric_variables)
```

```{r}
corrplot::corrplot(cor(numeric_variables), type = "upper", diag = FALSE)
```

```{r}
factor_variables = 
  birthweight %>%
  select(bwt, babysex, frace, malform, mrace) %>%
  mutate(
    babysex = as.numeric(babysex),
    frace = as.numeric(frace),
    malform = as.numeric(malform),
    mrace = as.numeric(mrace)
  )

corrplot::corrplot(cor(factor_variables), type = "upper", diag = FALSE)
```

We can tell from the plots that `bhead`, `blength`, `delwt`, `gaweeks`, `wtgain`, `frace` and `mrace` may have the biggest influence on birthweight.

Now fit the model using stepwise regression:
```{r}
intercept_only = lm(bwt ~ 1, data = birthweight)

biggest_model = lm(bwt ~ ., data = birthweight)

model_1 = step(intercept_only, direction='both', scope=formula(biggest_model), trace = 0)

equatiomatic::extract_eq(model_1, use_coefs = TRUE)
```
This model includes `bhead`, `blength`, `mrace`, `delwt`, `gaweeks`, `smoken`, `ppbmi`, `babysex`, `parity`, `ppwt` and `fincome`, more variables than I think have an influence on birthweight.

#### show a plot of model residuals against fitted values

```{r}
birthweight %>%
  add_predictions(model_1) %>%
  add_residuals(model_1) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  labs(title = "model residuals against fitted values")
```
```{r}
# fit two other models
model_2 = lm(bwt ~ gaweeks + blength, data = birthweight)
model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight)
```

#### Compare my model to two others:

```{r}
cv = 
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>% 
  mutate(
   model_1 = map(.x = train, ~lm(formula(model_1), data = .x)),
   model_2 = map(.x = train, ~lm(formula(model_2), data = .x)),
   model_3 = map(.x = train, ~lm(formula(model_3), data = .x))
  ) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = model_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = model_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = model_3, .y = test, ~rmse(model = .x, data = .y))
  )
```
Using violin plots to show comparison among three models
```{r}
cv %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```

From the plot we can tell that our model has the lowest rmse, which indicates its prediction is most reliable among them all, and the model only contains `gaweeks` and `blength` has the worst result, it looks like the more variable we include in our model, the better it would be. But we still need taking deeper investigation into this problem to find the best model.